\section{Project Organization}

This chapter aims to provide an overview of our internal project organization. Firstly, we are going to cover our software development cycle. We will then provide brief descriptions on the methods and technologies we used to help us maintain the best practices in our software development cycle.

We chose to follow an agile software development methodology and we used SCRUM as our framework. We mainly chose SCRUM due to the nature of our project - it is a highly complex and potentially huge project, and we needed regular feedback from our supervisor. SCRUM encourages short, iterative sprints, weekly meetings, and daily stand-ups. In addition to that, the number of members in the group seems very appropriate for SCRUM. Hence, we made SCRUM the backbone of our project organization.

As we have been given a fixed schedule for the project, we were able to create two iterative cycles, each cycle ending with a presentation of our current findings and results to everyone who takes part in the project. The cycle consists of brainstorming, research, implementation, and a demo.

In addition to our quarterly presentations, every two weeks we demonstrated the current prototype to our product owners, which were the project supervisors. Every week the team members, excluding the previous roles mentioned previously, met twice a week for a general discussion and sprint planning respectively. We chose to have shorter sprints (weekly), because we learned that it was very easy for us to lose track from the project goal. Hence, the weekly meeting helped us to stay on track. Moreover, we also had daily virtual stand-up meetings. This aimed to further prevent each other from going out of the scope, and for everyone to be more aware of what each member was doing at any given point in time, or if they were blocked with the current task, and required immediate reinforcements.

We used several technologies and mechanisms to aid us in following SCRUM with the best practices. One of the most important tools we used is ClickUp. ClickUp is a project management platform that helped us manage and track tasks, stories, epics, and sprints. During our sprint planning, our project manager would create all the necessary elements for the developers to start with their tasks. For example, creating a new sprint board, with all the members' tasks. The developers must then proceed with adding their own descriptions, user stories, and acceptance criteria into their own tasks. At the same time, the project manager could move and add tasks into and out of the backlog, depending on the resource allocation of each member for that sprint.

As the sprint started, ClickUp still played a huge role during the development phase. Another tool that we strongly leveraged on is GitHub, a version control for collaboration platform. Since each task is isolated, ClickUp allows users to track each commit and/or branch to each task, making our pull-requests organized, understandable and also isolated.

As a team, we also created a guideline on how to better isolate and organize branches, commits and ultimately the tasks themselves. For every task created on ClickUp, there was a unique identifier which we used to link the name of the branches and commits. For example,

\begin{itemize}
\item For branches: \_\#\{task id\}\_short\_description\_of\_branch.
\item For commits: \#\{task id\}\_commits\_message.
\end{itemize}


Once developers were done with their features, they created a pull request and they could move that specific task to the "QA" category in ClickUp for another developer to review the pull request. We made sure that we had at least two approvals before the pull request could be merged, and only that assigned reviewer could move the task to "Done".

We heavily relied on Slack and Google Hangouts for our day-to-day communication between team members, including the product owners, and our daily stand-up calls or messages.

Lastly, we used Google Drive to store our presentations, research documents, schedules, and most importantly, the meeting protocols. These protocols are created whenever there were more than three people meeting for the project. The protocol should contain all of the members present during that meeting, the agenda of the meeting, discussions, and next steps. The protocol helped project members to look back on what had been discussed in regards to design decisions and current or future tasks.


\newpage
