\subsection{Benchmarking for Use Cases}

(Maybe start text fancy with the questions which araise during the project: see the benchmarking google sheet for that)

- What did we benchmark?

Explain which scenarios we did test (1 employee, multiple employee)

Explain under which aspects we did benchmark (gas, time)

Explain the thing with benchmarking only the overhead due to automining of ganache

Mention again why gas is of utmost importance to us (because it translates to money and time)

- Insert graphics / statistics

Explain what is visible

Explain what that does mean

- Ellaborate on conclusions and findings from this evaluation

What do all the statistics say? what do they mean to us?

When does Off-Chaining make sense?

Do we really save gas?

-> Conclude on that

As already mentioned this project was carried out as a prototyping project. Therefore we need to benchmark our results against the current best practice. Current state of the art for deploying contracts to the ethereum blockchain includes saving all the state variables of the contract on the blockchain and thus on all machines participating in the blockchain. As proposed we want to save those state variables off from the blockchain and thus save on gas which explains why gas cost are our most important measurement.

We especially benchmarked the employee use case as the employee use case is the more complex one of our both use cases. As a preparation for benchmarking we first needed two different smart contracts. One smart contract that works completely on-chain without using any external database, hashing functions or merkle trees and another smart contract that uses all introduced methods that are needed in order to off-chain our data to an external database. The two variants behave completely similar except for the saving of the state variables. Both variants are completely functional and could be used as they are if someone would like to deploy the employee use case. These fact were very important to us because only like that we could make sure that our benchmarks lead to meaningful results. 

We mainly benchmarked the two measurements gas cost and time.

