\documentclass[a4paper]{article}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{float}


%% Sets page size and margins
\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

%% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{listings}

\setcounter{tocdepth}{4}
\setcounter{secnumdepth}{4}

\title{Off-chaining Smart Contract Data to DBMS}
\author{Thanh Tuan Tenh Cong, 
Simon Fallnich,
Patrick Friedrich,
Tarek Higazi,\\
Vincent Jonany,
Dukagjin Ramosaj,
Kevin Marcel Styp-Rekowski}

\begin{document}
\maketitle

\begin{abstract}

Blockchain technology is increasing in significance. Many organizations in different industries, though primarily in the Financial industry, have begun to explore the advantages of this revolutionary technology and how it could benefit their businesses. The potential outcomes of the Blockchain are tremendous and it appears that any industry that uses some sort of transaction, are likely to be disrupted by the Blockchain technology. Even though Blockchain’s based applications benefiting from Blockchain’s most important properties of immutability and transparency, there are also costs to be considered. With today’s Blockchain implementations, there are a few issues that need to be addressed such as storage capacities and data computation costs, performance and scalability issues. Through this research project, we motivated the need for off-chaining approaches to overcome today’s Blockchain limitations and to answer our research question on: “How can data used on-chain be outsourced to a Relational Database Management System (RDBMS) while compromising blockchain properties as little as possible”. Hence, we built a prototype as a proof-of-concept and analyzed how well our approach performs in terms of solving this problem. We find that using off-chaining approaches makes sense for specific use cases. Therefore, we introduced two potentially relevant use cases and analyzed our off-chaining reasoning further in this report. Moreover, we evaluated our implementation through detailed benchmarking results which support further our arguments on when it makes sense to use our off-chaining approach.


\end{abstract}
\newpage
\tableofcontents
\newpage

\input{sections/01_introduction}
\input{sections/02_background}
\input{sections/03_research_and_design}
\input{sections/04_off-chaining}
\input{sections/05_evaluation}
\input{sections/06_user_guide}
\input{sections/07_future_work}
\input{sections/08_project_organization}
\input{sections/09_conclusion}

\newpage
\bibliographystyle{unsrt}
\bibliography{sample}

\end{document}